Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-03-15 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added lit for explo-exploit

	\item Typically one-on-one \citep[also group-based; see,][]{McKenzie2021b}

@@

Learning styles
\begin{itemize_2pt}
	\item Psychological research finds interpersonal differences in \textcolor{bdf}{exploration-exploitation behavior} 
	\begin{itemize_2pt}
		\item Evidence for trait-like persistence of preference (see, e.g.,\textcolor{camel}{Waldner et al., 1998, Engler et al., 2010})%[citation]
		\item If technology has initial fixed costs, poverty \textit{per se} may affect trade-off
	\end{itemize_2pt}

>>>>

	\item Typically one-on-one \citep[also group-based; see,][]{Iacovone2021}

@@

Learning styles
\begin{itemize_2pt}
	\item Exploration-exploitation trade-off 
	\begin{itemize_2pt}

		\item Not clear how much to exploit available best practice, and how much to invest in search for innovation
		\item Psychological research finds interpersonal differences in \textcolor{bdf}{preference for information search} \cite[see, e.g.,][]{Hills2015, Schulz2020, Gonzalez2011}
		%\item Evidence for trait-like persistence of this preference (see, e.g.,\textcolor{camel}{Waldner et al., 1998, Engler et al., 2010})%[citation]
		\item If technology has initial fixed costs, poverty \textit{per se} may affect trade-off
	\end{itemize_2pt}
